%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{}{\Large Abdul Hazim Bin Abdul Majeed}} & Email : \href{mailto:abdhazim4343@gmail.com}{abdhazim4343@gmail.com}\\
  \href{https://www.linkedin.com/in/hazim4343/}{https://www.linkedin.com/in/hazim4343/} & Mobile : +60-10-463-8306 \\
  \href{https://github.com/zim96}{https://github.com/zim96} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Nottingham}{Nottingham, England, United Kingdom}
      {BSc (Hons) Computer Science with Artificial Intelligence;  First (70\%)}{Sep. 2017 -- Jul. 2018}
    \resumeSubheading
      {University of Nottingham Malaysia Campus}{Semenyih, Selangor, Malaysia}
      {BSc (Hons)  Computer Science with Artificial Intelligence;  First (77\%)}{Sep. 2015 -- Jul. 2017}
    \resumeSubheading
      {Universiti Malaya}{Kuala Lumpur, Malaysia}
      {Master of Computer Science (Applied Computing); GPA 3.30}{Sep. 2018 -- Aug. 2022}
  \resumeSubHeadingListEnd


%-----------WORK EXPERIENCE-----------------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Sunway XFarms}{Bandar Sunway, Selangor, Malaysia}
      {Data and Solutions Architect}{Jun. 2021 - Present}
      \resumeItemListStart
        \resumeItem{IoT Solutions}
          {Coordinating design and deployment of sensors and effectors to optimise farm operations}
        \resumeItem{FutureOS}
          {Develop and maintain a web application based on Vue, Express JS, Node JS, MongoDB and various other tools. A web application that provides a gateway to all farm operations}
        \resumeItem{Containerisation \& DevOps}
          {FutureOS runs on multiple hosts in Docker containers that are bound together by nginx. GitLab CI/CD and RedHat Ansible are used to maintain the applications' uptime}
      \resumeItemListEnd

    \resumeSubheading
      {BoomGrow Farms}{Taman Tun Dr Ismail, Kuala Lumpur, Malaysia}
      {Machine Intelligence Engineer}{Jan. 2019 - Feb. 2020}
      \resumeItemListStart
        \resumeItem{Imaging Solutions}
          {3D scanner using laser line triangulation. It's purpose is to scan seedlings to study and pick the ones that grow the fastest. Plant phenotyping chamber which captures images of plants for inspection and analysis.}
        \resumeItem{Embedded Development, IoT}
          {Various prototypes developed for various use cases. Familiar with I2C, UART, Ethernet communication. Also, worked with various sensors and actuators.}
        \resumeItem{Optimisation Algorithms}
	{Used Simulated Annealing to optmise the placement of LED chips on the board for optimal light distribution.}
        \resumeItem{MEAN Stack Backend}
	{RESTful API built using Node JS, Express JS, Mongoose and Postgresql for the various micro-services that will be deployed.}
        \resumeItem{Web Application}
	{Web Applications built using Vue.JS and Bootstrap as farm management software suite. Some interfaces serve as front-end for machines such as Plant Phenotyping Chamber.}
      \resumeItemListEnd
	
    \resumeSubheading
      {Crops for the Future Research Centre (CFFRC)}{Semenyih, Selangor, Malaysia}
      {Student Placement in the form of a Group Project}{Oct. 2016 - Apr. 2017}
      \resumeItemListStart
        \resumeItem{Google Cloud Platform}
          {The Google Cloud Platform is a suite of cloud computing services that runs on the same infrastructure that Google uses internally for its end-user products. At CFFRC, I mainly utilised the Google Maps API.}
        \resumeItem{LAMP Stack: Linux, Apache HTTP Server, MySQL, PHP}
          {LAMP is a web service/application model. At CFFRC, I utilised it to build 2 web applications which are part of the automated data-gap filling system.}
        \resumeItem{Soft Skills}
	{Being elected team leader allowed me to experience the real-world conditions in a Software Development team. It also was the opportunity to practice Software Engineering methodologies.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------

\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Image Processing \& Computer Vision}{Python, OpenCV, scikit-image, pytorch}
    \resumeSubItem{Machine Learning}{Python, scikit-learn, Scipy/Numpy}{R}
    \resumeSubItem{Deep Learning}{Python, tensorflow, keras}
    \resumeSubItem{Databases \& Web Applications}{MySQL, MongoDB}{JavaScript, NodeJS, VueJS}
    \resumeSubItem{Deployment \& DevOps}{Google Cloud, AWS, Docker, RedHat Ansible, Gitlab CI/CD, Nginx}
    \resumeSubItem{Embedded}{Raspberry Pi, Arduino, ESP32}
    \resumeSubItem{Misc.}{MATLAB}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Noteworthy Recent Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Blender 3D graphics and 3D reconstruction methods [Feb 2024]}{ Learning the skill of 3D modelling whilst applying 3D reconstruction methods including newer ones that I am unfamiliar with such as Neural Radiance Fields and Gaussian Splatting }
    \resumeSubItem{Astronomy \& Astrophotography [2023]}{ Venturing into the world of imaging the night sky using a 6 inch Newtonian Reflector telescope and various cameras }
    \resumeSubItem{Plant biotic stress detection and severity estimation [Sept 2021]}{Exploring the use of Machine Learning and Computer Vision for detection of weeds, diseases, etc.}
    \resumeSubItem{Facewear/Headwear Detection [Sept 2020]}{Project to detect facial wear such as masks, goggles, hats, etc.}
    \resumeSubItem{Decolourisation Algorithms [Apr 2020]}{Explored some of the different decolorisation algorithms that may improve performance of image processing tasks.}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
