%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Classicthesis-Styled CV
% LaTeX Template
% Version 1.0 (22/2/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Alessandro Plasmati
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{scrartcl}

\reversemarginpar % Move the margin to the left of the page 

\newcommand{\MarginText}[1]{\marginpar{\raggedleft\itshape\small#1}} % New command defining the margin text style

\usepackage[nochapters]{classicthesis} % Use the classicthesis style for the style of the document
\usepackage[LabelsAligned]{currvita} % Use the currvita style for the layout of the document

\renewcommand{\cvheadingfont}{\LARGE\color{Maroon}} % Font color of your name at the top

\usepackage{hyperref} % Required for adding links	and customizing them
\hypersetup{colorlinks, breaklinks, urlcolor=Maroon, linkcolor=Maroon} % Set link colors

\newlength{\datebox}\settowidth{\datebox}{Spring 2011} % Set the width of the date box in each block

\newcommand{\NewEntry}[3]{\noindent\hangindent=2em\hangafter=0 \parbox{\datebox}{\small \textit{#1}}\hspace{1.5em} #2 #3 % Define a command for each new block - change spacing and font sizes here: #1 is the left margin, #2 is the italic date field and #3 is the position/employer/location field
\vspace{0.5em}} % Add some white space after each new entry

\newcommand{\Description}[1]{\hangindent=2em\hangafter=0\noindent\raggedright\footnotesize{#1}\par\normalsize\vspace{1em}} % Define a command for descriptions of each entry - change spacing and font sizes here

%----------------------------------------------------------------------------------------

\begin{document}

\thispagestyle{empty} % Stop the page count at the bottom of the first page

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\begin{cv}{\spacedallcaps{Abdul Hazim}}\vspace{1.5em} % Your name

\Description{"Learn and Innovate for the betterment of the World"} % Goal text

\noindent\spacedlowsmallcaps{Personal Information}\vspace{0.5em} % Personal information heading

\NewEntry{}{\textit{Batu Caves, Selangor}} % Location Info

\NewEntry{email}{\href{mailto:abdhazim4343@gmail.com}{abdhazim4343@gmail.com}} % Email address

\NewEntry{website}{\href{http://abdulhazim.wordpress.com}{http://abdulhazim.wordpress.com}} % Personal website

\NewEntry{phone}{(MY) +60 (0)10 463 8306 } % Phone number(s)

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\noindent\spacedlowsmallcaps{Work Experience}\vspace{1em}

\NewEntry{2016}{2\textsuperscript{nd} Year Project-CropBase Gap Filler}

\Description{\MarginText{Crops for the Future}Developed a conceptual database gap filler framework and 
implemented some helper programs for the database of underutilised crops. \\ Reference: K R \textsc{Selvaraj}\ \ $\cdotp$\ \ \href{mailto:kr.selvaraj@nottingham.edu.my}{kr.selvaraj@nottingham.edu.my}}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Education}\vspace{1em}

\NewEntry{2018-Present}{Universiti Malaya}

\Description{\MarginText{Master of Computer Science}\textit{Applied Computing (Aritificial Intelligence)}\ \ $\cdotp$\ \ Faculty: Computer Science and Information Technology\newline
Curriculum:
\begin{itemize}
    \item Computer Vision and Image Processing
    \item Robotics and Intelligent agents
    \item Research Methods and Dissertation
\end{itemize}}

%-------------------------------------------------

\NewEntry{2017-2018}{University of Nottingham}

\Description{\MarginText{Bachelor of Science (cont)}Percentage: 70\%\ \ $\cdotp$\ \ \textit{Computer Science with Aritificial Intelligence}\ \ $\cdotp$\ \ School: Computer Science\newline
References: Assoc. Prof.~Gail \textsc{Hopkins} \& Assist. Prof.~Ender \textsc{{\"O}zcan}\newline\newline
Curriculum:
\begin{itemize}
    \item Machine Learning
    \item Search and Optimisation
    \item Computer Vision
    \item Designing Intelligent agents
    \item Computer Security
    \item Professional Ethics in Computing
\end{itemize}}

%------------------------------------------------
\NewEntry{2015-2017}{The University of Nottingham Malaysia Campus}

\Description{\MarginText{Bachelor of Science}Percentage: 77\%\ \ $\cdotp$\ \ \textit{Computer Science with Artificial Intelligence}\ \ $\cdotp$\ \ School: Computer Science\newline
References: Assist. Prof.~K R \textsc{Selvaraj} \& Assoc. Prof.~Tomas \textsc{Maul}\newline\newline
Curriculum:
\begin{itemize}
    \item C, Java and Haskell
    \item Operating Systems and Concurrency
    \item Software Engineering Methodologies
    \item Databases and Interfaces (MySQL, PHP, JavaScript, HTML, CSS)
    \item Artificial Intelligence (Search, Optimisation, Scheduling)
    \item Human Computer Interaction
\end{itemize}}

%----------------------------------------------------------------------------------------
%	NOTABLE PROJECTS
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Recent Notable Projects}\vspace{1em}

\NewEntry{Nov 2018}{'Bokeh' using Stereo Vision}

\Description{\MarginText{Stereo Vision Application}\newline 
Produce the highly sought after shallow depth of field effect (Bokeh) on photos using computer vision approach with binocular stereo vision. The additional depth information available in a stereo image could produce higher quality effects. Its' an effect widely implemented in today's cameras including smartphones but there is significant gap in publicly available academic documentation. Essentially, the depth map is produced using various available techniques including local and global methods. This is to explore the pros and cons of each method.}

%------------------------------------------------

\NewEntry{April 2018}{Comparisons of Stereo Correspondence Algorithms}

\Description{\MarginText{Stereo Vision}\newline 
Implement and visually inspect the disparity maps produced by different stereo correspondence algorithms. Algorithms include local and global methods to fully explore the processing time and quality of end-result. To start, simple block matching is used starting with Sum of Squared Differences (SSD) followed by the use of Feature Descriptors such as Gradients and Speeded Up Robust Features (SURF). The widely known Dynamic Programming approach is also implemented.}

%------------------------------------------------

\NewEntry{March 2018}{Active vs Passive Coordination in Distributive Foraging Reflexive Multi-Agent System}

\Description{\MarginText{Multi-Agent System}\newline 
Active and Passive coordination methods are tested in a Multi-Agent System built from a previous project, Utility-Reflex Foraging Agent. Utility-Reflex Foraging Agent is a reflex agent with utility functions to allow it to make more informed decisions about its foraging tasks. It is seen that it performs better than a Simple Relfex Agent. Additionally, exploration techniques was also experimented to learn the most efficient method to spread out agents. These two elements will ensure competition among agents is minimised thus increasing the foraging efficiency.}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Skills}\vspace{1em}

\Description{\MarginText{Basic}\textsc{python}, \textsc{Haskell}, \LaTeX, Android}

\Description{\MarginText{Intermediate}\textsc{matlab}, \textsc{c++}, \textsc{c}, \textsc{r}, \textsc{lamp}, Linux (Ubuntu/Debian), Stereo Vision, Machine Learning}

\Description{\MarginText{Advanced}\textsc{java}, Computer Hardware and Support, Microsoft Windows}

%----------------------------------------------------------------------------------------
%	OTHER INFORMATION
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Other Information}\vspace{1em}

\Description{2013\ \ $\cdotp$\ \ Industrial Arts Award - Recognition by my secondary school for my efforts in representing the school in various innovation competitions}

\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{2013\ \ $\cdotp$\ \ SPM Top Achiever Award - Sijil Pelajaran Malaysia is Malaysia's equivalent of the GCE O-Level standard}
%------------------------------------------------

\vspace{1em}

\newlength{\langbox} % Create a new length for the length of languages to keep them equally spaced
\settowidth{\langbox}{English} % Length equals the length of "English" - if you have a longer language in your list put it here

\Description{\MarginText{Languages}\parbox{\langbox}{\textsc{English}}\ \ $\cdotp$\ \ \ Mothertongue}

\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{\parbox{\langbox}{\textsc{Malay}}\ \ $\cdotp$\ \ \ Advanced (speaking and writing)}

\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

%------------------------------------------------

\Description{\MarginText{Interests} Archery, Badminton and Football \ \ $\cdotp$\ \ Gaming (Strategy and Simulation) \ \ $\cdotp$\ \ Cooking and Baking \ \ $\cdotp$\ \ Visual Arts \ \ $\cdotp$\ \ Astronomy}

%----------------------------------------------------------------------------------------

\end{cv}

\end{document}